Leadership across cultures and contexts: an exploratory analysis

### 2020-05-10 leadership_across_cultures_contexts.Rmd
Added some interpretation and citations to discussion of variablility and subsistence.

<!-- NEED TO DO: ADD SOME REFS AND BRIEF INTERPRETATION FOR BELOW-->

Four leadership dimensions varied by subsistence strategy. There was more evidence that hunter-gatherer leaders lacked coercive authority compared to other leaders. There was more evidence that both hunter-gatherer and pastoralist leaders generated food surpluses, but less evidence that pastoralist leaders distributed food and other resources.  There was more evidence that leaders in communities with mixed subsistence strategies distributed resources and less that they were older.

>>>>

Four leadership dimensions varied by subsistence strategy. There was more evidence that hunter-gatherer leaders lacked coercive authority compared to other leaders, which supports much theory and ethnography discussing egalitarianism and the active resistance of hierarchy among hunter-gatherers [e.g., @boehm_hierarchy_1999;@boehm_purposive_2008; @woodburn_egalitarian_1982]. Reliance on a mobile and stochastic resource base is suggested to promote strong social norms of sharing [@peterson_demand_1993; @cashdan_egalitarianism_1980] and shape both resource transfer and partner preferences [c.f., @smith_friend_2018; @smith_hunter-gatherers_2018]. There was more evidence that both hunter-gatherer and pastoralist leaders generated food surpluses, but less evidence that pastoralist leaders distributed food and other resources. Thus, systematic ethnographic evidence supports the important role of provisioning resources by high status males among foragers [@wood_prestige_2006; @gurven_give_2005; @gurven_men_2009; @alger_paternal_2020]. However, there was more evidence that leaders in communities with mixed subsistence strategies distributed resources, which lends support to high status males using economic success and producitivity as a status-seeking strategy [@hawkes_showing_2002; @hawkes_family_2010].
